Dark matter halo concentrations with a bayesian approach

### 2014-09-22 paper/article.tex
changed quote to italics

In Figure \ref{fig:error} we plotted $\xi$ for the three methods. We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos. On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods. As mentioned in FIXME "for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile." This fact could explain why $\xi$ increases with the number of particles for the density method.

>>>>

In Figure \ref{fig:error} we plotted $\xi$ for the three methods. We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos. On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods. As mentioned in FIXME \textit{``for a large fraction of halos, and for the most massive in particular, the NFW functional does not Represent a good fit to the density profile."} This fact could explain why $\xi$ increases with the number of particles for the density method.
